### 2019-08-01 paper/paper.tex
Some more clarifications

There are several photo-realistic renderers available which contain a vast amount of implicit knowledge. Differentiation allows such renderers to make use of gradients to learn the inverse mapping from an image to its parameter space. We can then use this knowledge in combination with any machine learning / deep learning models to train them in a fast and efficient manner. Experiments in~\cite{retinaface} demonstrate the effectiveness of incorporating differentiable renderers in deep learning pipelines by achieving State of the Art results in WIDERFace Hard dataset.

However, as usual, it is difficult to compute efficient derivatives from a production-ready renderer, typically written in a performance language like C++. This provides the primary motivation towards the development of RayTracer.jl. We develop an entire general purpose ray tracer in a high-level numerical computation language. The presence of strong automatic differentiation libraries like Zygote.jl make it trivial to compute efficient derivatives from the renderer.We present the performance gains we get on using Zygote as compared to Central Differencing in Section~\ref{sec:finite_diff}.

@@

In this section, we compare the use of our source-to-source AD backend with Central Finite Differencing, that is built into the package for gradient testing purposes. For comparing the two differentiation techniques, we run five independent trails and present the mean runtimes (with the standard deviation) in Figure~\ref{fig:ad_better}.

We fix the position of the camera and light and randomly generate the triangles present in the scene. Every new triangle added to the scene, adds 20 additional parameters with respect to which we must compute the derivatives. We use the mean squared loss function to compute the scalar loss and backpropagate.

>>>>

There are several photo-realistic renderers available which contain a vast amount of implicit knowledge. Differentiation allows such renderers to make use of gradients to learn the inverse mapping from an image to its parameter space. However as usual, it is difficult to compute efficient derivatives from a production-ready renderer, typically written in a performance language like C++. This provides the primary motivation towards the development of RayTracer.jl. We develop an entire general purpose ray tracer in a high-level numerical computation language. The presence of strong automatic differentiation libraries like Zygote.jl make it trivial to compute efficient derivatives from the renderer. We present the performance gains we get on using Zygote as compared to Central Differencing in Section~\ref{sec:finite_diff}.

@@

In this section, we demonstrate the performance gain of using source-to-source AD backend versus Central Finite Differencing, that is built into the package for gradient testing purposes. Through this experiment we show that our method is exponentially better than numerical differentiation.

For comparing the two differentiation techniques, we run five independent trails and present the mean runtimes (with the standard deviation) in Figure~\ref{fig:ad_better}. We fix the position of the camera and light and randomly generate the triangles present in the scene. Every new triangle added to the scene, adds 20 additional parameters with respect to which we must compute the derivatives. We use the mean squared loss function to compute the scalar loss and backpropagate.
